Analysis on Movie Success Indicators

### 2024-04-14 paper/paper.qmd
going over figures

---
title: "Analysis on Movie Success Indicators"
author: 
  - Qi Er (Emma) Teng
thanks: "Code and data are available at: https://github.com/dwz92/Analysis-on-Movie-Success-Indicators."
date: today
date-format: long
abstract: "In this study, we delve into the variables contributing to movie success, focusing on the interplay between a movies’ genre, number of theaters showing, the moth of release, and the year of premiere, particularly in the context of the pre and post-COVID-19 era, spanning from 2019 to 2022. This comprehensive analysis aims to shed light on the nuanced relationship between these variables and movie success, highlighting how the cinematic landscape has evolved in response to the COVID-19 pandemic. The findings of this study enrich our understanding of the determinants of cinematic success, providing valuable insights for filmmakers, distributors, and industry strategists in navigating the changing film industry."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)
library(dplyr)
library(arrow)
library(here)
library(kableExtra)
```

@@

mov1922 |>
  select(release, release_year, release_date, theaters, total_gross) |>
  slice(1:10) |>
  kable(
    colnames = c("Title", "Release Year", "Release Date", "Released Theaters", "Total Gross Value"),
    booktabs = TRUE
  )

@@

titlebasic |>
  select(originalTitle, startYear, genres, tconst) |>
  kable(
    colnames = c("Title", "Release Year", "Genres", "IMDb primary key"),
    booktabs = TRUE
  )
```

@@

titlerate |>
  select(averageRating, numVotes, tconst) |>
  kable(
    colnames = c("Rating", "Number of Votes", "IMDb primary key"),
    booktabs = TRUE
  )
```

@@

movcomb |>
  select(release, release_year, release_date, genres, averageRating, theaters) |>
  slice(1:10) |>
  kable(
    colnames = c("Title", "Release Year", "Release Date", "Genres", "Rating", "Released Theaters"),
    booktabs = TRUE
  )
```

@@

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

>>>>

---
title: "Analysis on Movie Success Indicators"
author: 
  - Qi Er (Emma) Teng
thanks: "Code and data are available at: https://github.com/dwz92/Analysis-on-Movie-Success-Indicators."
date: today
date-format: long
abstract: "In this study, we delve into the variables contributing to movie success, focusing on the interplay between a movies’ genre, number of theaters showing, the moth of release, and the year of premiere, particularly in the context of the pre and post-COVID-19 era, spanning from 2019 to 2022. This comprehensive analysis aims to shed light on the nuanced relationship between these variables and movie success, highlighting how the cinematic landscape has evolved in response to the COVID-19 pandemic. The findings of this study enrich our understanding of the determinants of cinematic success, providing valuable insights for filmmakers, distributors, and industry strategists in navigating the changing film industry."
format: html
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)
library(dplyr)
library(arrow)
library(here)
library(kableExtra)
library(ggrepel)
```

@@

mov1922 |>
  select(release, release_year, release_date, theaters, total_gross) |>
  slice(1:10) |>
  kable(
    col.names = c("Title", "Release Year", "Release Date", "Released Theaters", "Total Gross Value"),
    booktabs = TRUE
  )

@@

titlebasic |>
  select(originalTitle, startYear, genres, tconst) |>
  kable(
    col.names = c("Title", "Release Year", "Genres", "IMDb primary key"),
    booktabs = TRUE
  )
```

@@

titlerate |>
  select(averageRating, numVotes, tconst) |>
  kable(
    col.names = c("Rating", "Number of Votes", "IMDb primary key"),
    booktabs = TRUE
  )
```

@@

movcomb |>
  select(release, release_year, release_date, genres, averageRating, theaters) |>
  slice(1:10) |>
  kable(
    col.names = c("Title", "Release Year", "Release Date", "Genres", "Rating", "Released Theaters"),
    booktabs = TRUE
  )
```

@@

```{r}
#| label: fig-2019-movie-success-genre
#| fig-cap: Movie Success in 2019 by Genre
#| echo: false
#| warning: false
#| message: false

df_long <- movcomb

df_long <- df_long |>
  filter(release_year == 2019) |>
  separate_rows(genres, sep = ",") |>
  mutate(genres = trimws(genres)) |>
  group_by(genres) |>
  summarise(

    averageRating = mean(averageRating, na.rm = TRUE),
    numRele = sum(theaters, na.rm = TRUE)
  )

# Create the plot
ggplot(df_long, aes(x = reorder(genres, numRele), y = averageRating, size = numRele, label = genres)) +
  geom_point(alpha = 0.5, color = "lightblue") +
  geom_text_repel(
    aes(label = genres),
    size = 5,  
    max.overlaps = Inf, 
    point.padding = NA,
    box.padding = 0.35,
    segment.color = NA 
  ) +
  scale_size_continuous(range = c(5, 30)) +
  geom_hline(yintercept = 7, linetype = "dashed", color = "red") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Genre", y = "Average Rating", title = "Movie Ratings by Genre in 2019")
```

```{r}
#| label: fig-2020-movie-success-genre
#| fig-cap: Movie Success in 2020 by Genre
#| echo: false
#| warning: false
#| message: false

df_long <- movcomb

df_long <- df_long |>
  filter(release_year == 2020) |>
  separate_rows(genres, sep = ",") |>
  mutate(genres = trimws(genres)) |>
  group_by(genres) |>
  summarise(

    averageRating = mean(averageRating, na.rm = TRUE),
    numRele = sum(theaters, na.rm = TRUE)
  )

# Create the plot
ggplot(df_long, aes(x = reorder(genres, numRele), y = averageRating, size = numRele, label = genres)) +
  geom_point(alpha = 0.5, color = "lightblue") +
  geom_text_repel(
    aes(label = genres),
    size = 5,  
    max.overlaps = Inf, 
    point.padding = NA,
    box.padding = 0.35,
    segment.color = NA 
  ) +
  scale_size_continuous(range = c(5, 30)) +
  geom_hline(yintercept = 7, linetype = "dashed", color = "red") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Genre", y = "Average Rating", title = "Movie Ratings by Genre in 2020")
```

```{r}
#| label: fig-2021-movie-success-genre
#| fig-cap: Movie Success in 2021 by Genre
#| echo: false
#| warning: false
#| message: false

df_long <- movcomb

df_long <- df_long |>
  filter(release_year == 2021) |>
  separate_rows(genres, sep = ",") |>
  mutate(genres = trimws(genres)) |>
  group_by(genres) |>
  summarise(

    averageRating = mean(averageRating, na.rm = TRUE),
    numRele = sum(theaters, na.rm = TRUE)
  )

# Create the plot
ggplot(df_long, aes(x = reorder(genres, numRele), y = averageRating, size = numRele, label = genres)) +
  geom_point(alpha = 0.5, color = "lightblue") +
  geom_text_repel(
    aes(label = genres),
    size = 5,  
    max.overlaps = Inf, 
    point.padding = NA,
    box.padding = 0.35,
    segment.color = NA 
  ) +
  scale_size_continuous(range = c(5, 30)) +
  geom_hline(yintercept = 7, linetype = "dashed", color = "red") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Genre", y = "Average Rating", title = "Movie Ratings by Genre in 2021")
```

```{r}
#| label: fig-2022-movie-success-genre
#| fig-cap: Movie Success in 2022 by Genre
#| echo: false
#| warning: false
#| message: false

df_long <- movcomb

df_long <- df_long |>
  filter(release_year == 2022) |>
  separate_rows(genres, sep = ",") |>
  mutate(genres = trimws(genres)) |>
  group_by(genres) |>
  summarise(

    averageRating = mean(averageRating, na.rm = TRUE),
    numRele = sum(theaters, na.rm = TRUE)
  )

# Create the plot
ggplot(df_long, aes(x = reorder(genres, numRele), y = averageRating, size = numRele, label = genres)) +
  geom_point(alpha = 0.5, color = "lightblue") +
  geom_text_repel(
    aes(label = genres),
    size = 5,  
    max.overlaps = Inf, 
    point.padding = NA,
    box.padding = 0.35,
    segment.color = NA 
  ) +
  scale_size_continuous(range = c(5, 30)) +
  geom_hline(yintercept = 7, linetype = "dashed", color = "red") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Genre", y = "Average Rating", title = "Movie Ratings by Genre in 2022")
```

@@

\begin{align} 
y_i|\mu_i &\sim \mbox{Bern}(\mu_i) \\
logit(\mu_i) &= \beta_0 + \beta_{y[i]}^{year} + \beta_{t[i]}^{theater} \\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_{y[i]}^{year} &\sim \mbox{Normal}(0, 2.5) for \space y = 2019, 2020, 2021, 2022 \\
\\beta_{t[i]}^{theater} &\sim  \mbox{Normal}(0, 2.5) for \space t = 0, T
\end{align}
